{{< var titll >}}

### 2024-07-09 index.qmd
abc
prerender
first

```{webr-r}
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
df <- ManifoldDestinyWASMD::yout
dplyr::select(df[[1]],S,T,U,V)
```

>>>>

```{webr-r}
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
library(ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
library(ManifoldDestinyWASMP)
ls(package:ManifoldDestinyWASMP)data(package='ManifoldDestinyWASMD')
```
